```{r, child = "setup.Rmd", include = FALSE}
```

`r descr_models("proportional_hazards", "glmnet")`

## Tuning Parameters

```{r glmnet-param-info, echo = FALSE}
defaults <- 
  tibble::tibble(parsnip = c("penalty", "mixture"),
                 default = c("see below", "1.0"))

param <-
proportional_hazards() %>% 
  set_engine("glmnet") %>% 
  tunable() %>% 
  dplyr::select(-source, -component, -component_id, parsnip = name) %>% 
  dplyr::mutate(
    dials = purrr::map(call_info, get_dials),
    label = purrr::map_chr(dials, ~ .x$label),
    type = purrr::map_chr(dials, ~ .x$type)
  ) %>% 
  dplyr::full_join(defaults, by = "parsnip") %>% 
  dplyr::mutate(
    item = 
      glue::glue("- `{parsnip}`: {label} (type: {type}, default: {default})\n\n")
  )
```

This model has `r nrow(param)` tuning parameters:

```{r glmnet-param-list, echo = FALSE, results = "asis"}
param$item
```

A value of `mixture = 1` corresponds to a pure lasso model, while `mixture = 0` indicates ridge regression.

The `penalty` parameter has no default and requires a single numeric value. For more details about this, and the `glmnet` model in general, see [parsnip::glmnet-details].

## Translation from parsnip to the original package

```{r glmnet-creg}
proportional_hazards(penalty = double(1), mixture = double(1)) %>% 
  set_engine("glmnet") %>% 
  translate()
```

## Preprocessing requirements

```{r child = "template-makes-dummies.Rmd"}
```

```{r child = "template-same-scale.Rmd"}
```
By default, [glmnet::glmnet()] uses the argument `standardize = TRUE` to center and scale the data. 

# References

 - Simon N, Friedman J, Hastie T, Tibshirani R. 2011. "Regularization Paths for Cox’s Proportional Hazards Model via Coordinate Descent." _Journal of Statistical Software_, Articles 39 (5): 1–13. \doi{10.18637/jss.v039.i05}.
 
 - Hastie T, Tibshirani R, Wainwright M. 2015. _Statistical Learning with Sparsity_. CRC Press.
 
 - Kuhn M, Johnson K. 2013. _Applied Predictive Modeling_. Springer.

