# Engine Details

```{r, child = "setup.Rmd", include = FALSE}
```

Engines may have pre-set default arguments when executing the model fit call. 
For this type of model, the template of the fit calls are below.

## flexsurv

```{r flexsurv-reg}
survival_reg() %>% 
  set_engine("flexsurv") %>% 
  set_mode("censored regression") %>% 
  translate()
```

## survival

```{r survival-reg}
survival_reg() %>% 
  set_engine("survival") %>% 
  set_mode("censored regression") %>% 
  translate()
```

Note that `model = TRUE` is needed to produce quantile predictions when there 
is a stratification variable and can be overridden in other cases.

`fit()` passes the data directly to `survival::curvreg()` so that its formula 
method can create dummy variables as-needed. 

## Parameter translations

The standardized parameter names in parsnip can be mapped to their original 
names in each engine that has main parameters. Each engine typically has a 
different default value (shown in parentheses) for each parameter.

```{r echo = FALSE, results = "asis"}
get_defaults_survival_reg <- function() {
  tibble::tribble(
    ~model,      ~engine,     ~parsnip,     ~original,  ~default,
    "survival_reg",  "flexsurv",  "dist",       "dist",     NA,
    "survival_reg",  "survival",  "dist",       "dist",     NA,
  )
}
convert_args("survival_reg")
```

