```{r, child = "setup.Rmd", include = FALSE}
```

`r descr_models("survival_reg", "flexsurv")`

## Tuning Parameters

```{r party-param-info, echo = FALSE}
defaults <- 
  tibble::tibble(parsnip = c("dist"),
                 default = c("'weibull'"))

param <-
  survival_reg() %>%
  set_engine("flexsurv") %>%
  set_mode("censored regression") %>%
  tunable() %>%
  dplyr::select(-source, -component, -component_id, parsnip = name) %>%
  dplyr::mutate(
    dials = purrr::map(call_info, get_dials),
    label = purrr::map_chr(dials, ~ .x$label),
    type = purrr::map_chr(dials, ~ .x$type)
  ) %>%
  dplyr::full_join(defaults, by = "parsnip") %>%
  dplyr::mutate(
    item =
      glue::glue("- `{parsnip}`: {label} (type: {type}, default: {default})\n\n")
  )
```


This model has `r nrow(param)` tuning parameters:

```{r party-param-list, echo = FALSE, results = "asis"}
param$item
```


## Translation from parsnip to the original package

```{r flexsurv-creg}
survival_reg() %>% 
  set_engine("flexsurv") %>% 
  set_mode("censored regression") %>% 
  translate()
```

## Other details

For this engine, stratification cannot be specified via [`strata()`], please 
see the documentation of the [`flexsurv`] package for alternative 
specifications.

## References

- Jackson, C. 2016. `flexsurv`: A Platform for Parametric Survival  Modeling in R. _Journal of Statistical Software_, 70(8), 1 - 33.
