---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# censored

<!-- badges: start -->
[![R-CMD-check](https://github.com/tidymodels/censored/workflows/R-CMD-check/badge.svg)](https://github.com/tidymodels/censored/actions)
[![Codecov test coverage](https://codecov.io/gh/tidymodels/censored/branch/main/graph/badge.svg)](https://codecov.io/gh/tidymodels/censored?branch=main)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental) 
<!-- badges: end -->

`censored` is a [parsnip](https://parsnip.tidymodels.org) extension package which provides engines for various models for censored regression and survival analysis.

## Installation

This package is still in development. You can install the development version with

``` {.r}
devtools::install_github("tidymodels/censored")
```

# Available models, engines, and prediction types 

censored provides engines for the models in the following table. 

The time to event can be predicted with `type = "time"`, the 
survival probability with `type = "survival"`, the linear predictor with `type = "linear_pred"`, the quantiles of the event time distribution with `type = "quantile"`, and the hazard with `type = "hazard"`.

```{r, echo=FALSE, message=FALSE}
library(censored)
library(dplyr)
library(purrr)
library(tidyr)

yep <- cli::symbol$tick
nope <- cli::symbol$cross

mod_names <- get_from_env("models")
model_info <-
  map_dfr(mod_names, ~ get_from_env(paste0(.x, "_predict")) %>% mutate(alias = .x))

model_info %>%
  filter(mode == "censored regression") %>%
  select(model = alias, engine, mode, type, -value) %>%
  pivot_wider(names_from = type, 
              values_from = mode, 
              values_fill = nope, 
              values_fn = function(x) yep) %>%
  knitr::kable()
```
