---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# censored

<!-- badges: start -->
[![R-CMD-check](https://github.com/EmilHvitfeldt/censored/workflows/R-CMD-check/badge.svg)](https://github.com/EmilHvitfeldt/censored/actions)
[![Codecov test coverage](https://codecov.io/gh/EmilHvitfeldt/censored/branch/master/graph/badge.svg)](https://codecov.io/gh/EmilHvitfeldt/censored?branch=master)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental) 

<!-- badges: end -->

`censored` is a “`parsnip`-adjacent” packages with
model definitions for censored regression and survival analysis models.

## Installation

This package is still in early development. You need to install the developmental branch of parsnip as well.

``` {.r}
# install.packages("pak")
pak::pak("EmilHvitfeldt/censored")
```

## Prediction Types

The addition of censored regression comes with changes. One of these changes is the quantities we would like to predict from the model. The 3 quantities we will consider are: `"time"`, `"survival"`, and `"linear_pred"`.

To showcase these the differences, here is a simple Cox regression model fitted on the `lung` data set.

```{r}
library(censored)
library(survival)

cox_mod <-
  cox_reg() %>%
  set_engine("survival") %>%
  fit(Surv(time, status) ~ age + ph.ecog, data = lung)

cox_mod
```

### time

when we specify `type = "time"` then we get back the predicted survival time of an observation based on its predictors. The survival time is the time it takes for the observation to observe an event.

```{r}
predict(cox_mod, type = "time", new_data = head(lung))
```

Here we see that the first patient is predicted to have `r round(predict(cox_mod, type = "time", new_data = lung)$.pred_time[1], 2)` days left.

### survival

when we specify `type = "survival"` then we are trying to get the probabilities of survival (not observing an event) up to a given time `.time`. 

```{r}
pred_vals_survival <- predict(cox_mod, 
                              type = "survival", 
                              new_data = head(lung), 
                              .time = c(100, 200))

pred_vals_survival

pred_vals_survival$.pred[[1]]
```

here we see that the first patient has a `r round(pred_vals_survival$.pred_survival[[1]]$.pred_survival[1], 3) * 100`% probability of survival after 100 days and `r round(pred_vals_survival$.pred_survival[[1]]$.pred_survival[2], 3) * 100`%
probability of survival after 200 days.

### linear_pred

when we specify `type = "linear_pred"` then we get back the linear predictor for the observation according to the model.

```{r}
predict(cox_mod, type = "linear_pred", new_data = head(lung))
```

here we see that the linear predictor of the first observation is  `r round(predict(cox_mod, type = "linear_pred", new_data = lung)$.pred_linear_pred[1], 4)`.

## Prediction type table 

```{r, echo=FALSE, message=FALSE}
library(censored)
library(dplyr)
library(purrr)
library(tidyr)
mod_names <- get_from_env("models")
model_info <-
  map_dfr(mod_names, ~ get_from_env(paste0(.x, "_predict")) %>% mutate(alias = .x))

model_info %>%
  filter(mode == "censored regression") %>%
  select(alias, engine, mode, type, -value) %>%
  pivot_wider(names_from = type, 
              values_from = mode, 
              values_fill = FALSE, 
              values_fn = function(x) TRUE) %>%
  knitr::kable()
```

