---
title: "Fitting and Predicting with censored"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Fitting and Predicting with censored}
output:
  knitr:::html_vignette
---

```{r startup, include = FALSE}
library(utils)
library(ggplot2)
theme_set(theme_bw())
```

These examples illustrate which models, engines, and prediction types are available in censored. As a reminder, in parsnip, 

- the **model type** differentiates basic modeling approaches, such as random forests, proportional hazards models, etc.,

- the **mode** denotes in what kind of modeling context it will be used (here, censored regression), and

- the computational **engine** indicates how the model is fit, such as with a specific R package implementation or even methods outside of R like Keras or Stan.

The following examples use the same data set throughout.


## `bag_tree()` models
  
  <details id="bag-tree-rpart"> 
  
  <summary>With the `"rpart"` engine</summary>
  
  ```{r echo=FALSE}
  knitr::spin_child("template-lung.R")
  ```

  We can define the model with specific parameters:
  
  ```{r}
  bt_spec <- 
    bag_tree(cost_complexity = 0) %>%
    set_engine("rpart") %>% 
    set_mode("censored regression") 
  bt_spec
  ```

  Now we create the model fit object:
  
  ```{r}
  set.seed(1)
  bt_fit <- bt_spec %>% fit(Surv(time, status) ~ ., data = lung_train)
  bt_fit
  ```

  The holdout data can be predicted for survival probability at different time points as well as event time.
  
  ```{r}
  predict(
    bt_fit, 
    lung_test, 
    type = "survival", 
    eval_time = c(100, 500, 1000)
  ) %>% 
    slice(1) %>% 
    tidyr::unnest(col = .pred)
  predict(bt_fit, lung_test, type = "time")
  ```
  
  </details>


## `boost_tree()` models
  
  <details id="boost-tree-mboost"> 
  
  <summary>With the `"mboost"` engine</summary>
  
  ```{r echo=FALSE}
  knitr::spin_child("template-lung.R")
  ```

  We can define the model with specific parameters:
  
  ```{r}
  bt_spec <- 
    boost_tree(trees = 15) %>%
    set_engine("mboost") %>% 
    set_mode("censored regression") 
  bt_spec
  ```

  Now we create the model fit object:
  
  ```{r}
  set.seed(1)
  bt_fit <- bt_spec %>% fit(Surv(time, status) ~ ., data = lung_train)
  bt_fit
  ```

  The holdout data can be predicted for survival probability at different time points as well as the linear predictor.
  
  ```{r}
  predict(
    bt_fit, 
    lung_test,
    type = "survival",
    eval_time = c(100, 500, 1000)
  ) %>% 
    slice(1) %>% 
    tidyr::unnest(col = .pred)
  predict(bt_fit, lung_test, type = "linear_pred")
  ```
  
  </details>


## `decision_tree()` models
  
  <details id="decision-tree-rpart"> 
  
  <summary>With the `"rpart"` engine</summary>
  
  ```{r echo=FALSE}
  knitr::spin_child("template-lung.R")
  ```

  We can define the model with specific parameters:
  
  ```{r}
  dt_spec <- 
    decision_tree(cost_complexity = 0) %>%
    set_engine("rpart") %>% 
    set_mode("censored regression") 
  dt_spec
  ```

  Now we create the model fit object:
  
  ```{r}
  set.seed(1)
  dt_fit <- dt_spec %>% fit(Surv(time, status) ~ ., data = lung_train)
  dt_fit
  ```

  The holdout data can be predicted for survival probability at different time points as well as event time.
  
  ```{r}
  predict(
    dt_fit, 
    lung_test, 
    type = "survival",
    eval_time = c(100, 500, 1000)
  ) %>% 
    slice(1) %>% 
    tidyr::unnest(col = .pred)
  predict(dt_fit, lung_test, type = "time")
  ```
  
  </details>
  
  <details id="decision-tree-partykit"> 
  
  <summary>With the `"partykit"` engine</summary>
  
  ```{r echo=FALSE}
  knitr::spin_child("template-lung.R")
  ```

  We can define the model with specific parameters:
  
  ```{r}
  dt_spec <- 
    decision_tree() %>%
    set_engine("partykit") %>% 
    set_mode("censored regression") 
  dt_spec
  ```

  Now we create the model fit object:
  
  ```{r}
  set.seed(1)
  dt_fit <- dt_spec %>% fit(Surv(time, status) ~ ., data = lung_train)
  dt_fit
  ```

  The holdout data can be predicted for survival probability at different time points as well as event time.
  
  ```{r}
  predict(
    dt_fit, 
    lung_test, 
    type = "survival",
    eval_time = c(100, 500, 1000)
  ) %>% 
    slice(1) %>% 
    tidyr::unnest(col = .pred)
  predict(dt_fit, lung_test, type = "time")
  ```
  
  </details>


## `proportional_hazards()` models
  
  <details id="proportional-hazards-survival"> 
  
  <summary>With the `"survival"` engine</summary>
  
  ```{r echo=FALSE}
  knitr::spin_child("template-lung.R")
  ```

  We can define the model with specific parameters:
  
  ```{r}
  ph_spec <- 
    proportional_hazards() %>%
    set_engine("survival") %>% 
    set_mode("censored regression") 
  ph_spec
  ```

  Now we create the model fit object:
  
  ```{r}
  set.seed(1)
  ph_fit <- ph_spec %>% fit(Surv(time, status) ~ ., data = lung_train)
  ph_fit
  ```

  The holdout data can be predicted for survival probability at different time points as well as the linear predictor and event time.
  
  ```{r}
  predict(
    ph_fit, 
    lung_test, 
    type = "survival",
    eval_time = c(100, 500, 1000)
  ) %>% 
    slice(1) %>% 
    tidyr::unnest(col = .pred)
  predict(ph_fit, lung_test, type = "linear_pred")
  predict(ph_fit, lung_test, type = "time")
  ```
  
  </details>
  
  <details id="proportional-hazards-glmnet"> 
  
  <summary>With the `"glmnet"` engine</summary>
  
  ```{r echo=FALSE}
  knitr::spin_child("template-lung.R")
  ```

  We can define the model with specific parameters:
  
  ```{r}
  ph_spec <- 
    proportional_hazards(penalty = 0.1) %>%
    set_engine("glmnet") %>% 
    set_mode("censored regression") 
  ph_spec
  ```

  Now we create the model fit object:
  
  ```{r}
  set.seed(1)
  ph_fit <- ph_spec %>% fit(Surv(time, status) ~ ., data = lung_train)
  ph_fit
  ```

  The holdout data can be predicted for survival probability at different time points as well as the linear predictor.
  
  ```{r}
  predict(
    ph_fit, 
    lung_test, 
    type = "survival",
    eval_time = c(100, 500, 1000)
  ) %>% 
    slice(1) %>% 
    tidyr::unnest(col = .pred)
  predict(ph_fit, lung_test, type = "linear_pred")
  ```
  
  </details>


## `rand_forest()` models
  
  <details id="rand-forest-partykit"> 
  
  <summary>With the `"partykit"` engine</summary>
  
  ```{r echo=FALSE}
  knitr::spin_child("template-lung.R")
  ```

  We can define the model with specific parameters:
  
  ```{r}
  rf_spec <- 
    rand_forest(trees = 200) %>%
    set_engine("partykit") %>% 
    set_mode("censored regression") 
  rf_spec
  ```

  Now we create the model fit object:
  
  ```{r}
  set.seed(1)
  rf_fit <- rf_spec %>% fit(Surv(time, status) ~ ., data = lung_train)
  rf_fit
  ```

  The holdout data can be predicted for survival probability at different time points as well as event time.
  
  ```{r}
  predict(
    rf_fit, 
    lung_test, 
    type = "survival", 
    eval_time = c(100, 500, 1000)
  ) %>% 
    slice(1) %>% 
    tidyr::unnest(col = .pred)
  predict(rf_fit, lung_test, type = "time")
  ```
  
  </details>
  
  <details id="rand-forest-aorsf"> 
  
  <summary>With the `"aorsf"` engine</summary>
  
  ```{r echo=FALSE}
  knitr::spin_child("template-lung.R")
  ```

  We can define the model with specific parameters:
  
  ```{r}
  rf_spec <- 
    rand_forest(trees = 200) %>%
    set_engine("aorsf") %>% 
    set_mode("censored regression") 
  rf_spec
  ```

  Now we create the model fit object:
  
  ```{r}
  set.seed(1)

  rf_fit <- rf_spec %>% fit(Surv(time, status) ~ ., data = lung_train)
  rf_fit
  ```

  The holdout data can be predicted for survival probability at different time points as well as event time.
  
  ```{r}
  predict(
    rf_fit, 
    lung_test, 
    type = "survival", 
    eval_time = c(100, 500, 1000)
  ) %>% 
    slice(1) %>% 
    tidyr::unnest(col = .pred)
  predict(rf_fit, lung_test, type = "time")
  ```
  </details>
  
  
## `survival_reg()` models
  
  <details id="survival-reg-survival"> 
  
  <summary>With the `"survival"` engine</summary>
  
  ```{r echo=FALSE}
  knitr::spin_child("template-lung.R")
  ```

  We can define the model with specific parameters:
  
  ```{r}
  sr_spec <- 
    survival_reg(dist = "weibull") %>%
    set_engine("survival") %>% 
    set_mode("censored regression") 
  sr_spec
  ```

  Now we create the model fit object:
  
  ```{r}
  set.seed(1)
  sr_fit <- sr_spec %>% fit(Surv(time, status) ~ ., data = lung_train)
  sr_fit
  ```

  The holdout data can be predicted for survival probability at different time points as well as event time, linear predictor, quantile, and hazard.
  
  ```{r}
  predict(
    sr_fit, 
    lung_test, 
    type = "survival",
    eval_time = c(100, 500, 1000)
  ) %>% 
    slice(1) %>% 
    tidyr::unnest(col = .pred)
  predict(sr_fit, lung_test, type = "time")
  predict(sr_fit, lung_test, type = "linear_pred")
  predict(sr_fit, lung_test, type = "quantile")
  predict(sr_fit, lung_test, type = "hazard", eval_time = c(100, 500, 1000)) %>% 
    slice(1) %>% 
    tidyr::unnest(col = .pred)
  ```
  
  </details>

  <details id="survival-reg-flexsurv"> 
  
  <summary>With the `"flexsurv"` engine</summary>
  
  ```{r echo=FALSE}
  knitr::spin_child("template-lung.R")
  ```

  We can define the model with specific parameters:
  
  ```{r}
  sr_spec <- 
    survival_reg(dist = "weibull") %>%
    set_engine("flexsurv") %>% 
    set_mode("censored regression") 
  sr_spec
  ```

  Now we create the model fit object:
  
  ```{r}
  set.seed(1)
  sr_fit <- sr_spec %>% 
    fit(Surv(time, status) ~ age + sex + ph.ecog, data = lung_train)
  sr_fit
  ```

  The holdout data can be predicted for survival probability at different time points as well as event time, linear predictor, quantile, and hazard. 
  
  ```{r}
  predict(
    sr_fit, 
    lung_test, 
    type = "survival",
    eval_time = c(100, 500, 1000)
  ) %>% 
    slice(1) %>% 
    tidyr::unnest(col = .pred)
  predict(sr_fit, lung_test, type = "time")
  predict(sr_fit, lung_test, type = "linear_pred")
  predict(sr_fit, lung_test, type = "quantile")
  predict(sr_fit, lung_test, type = "hazard", eval_time = c(100, 500, 1000)) %>% 
    slice(1) %>% 
    tidyr::unnest(col = .pred)
  ```
  
  </details>
  
  <details id="survival-reg-flexsurvspline"> 
  
  <summary>With the `"flexsurvspline"` engine</summary>
  
  ```{r echo=FALSE}
  knitr::spin_child("template-lung.R")
  ```

  We can define the model:
  
  ```{r}
  sr_spec <- 
    survival_reg() %>%
    set_engine("flexsurvspline") %>% 
    set_mode("censored regression") 
  sr_spec
  ```

  Now we create the model fit object:
  
  ```{r}
  set.seed(1)
  sr_fit <- sr_spec %>% 
    fit(Surv(time, status) ~ age + sex + ph.ecog, data = lung_train)
  sr_fit
  ```

  The holdout data can be predicted for survival probability at different time points as well as event time, linear predictor, quantile, and hazard. 
  
  ```{r}
  predict(
    sr_fit, 
    lung_test, 
    type = "survival",
    eval_time = c(100, 500, 1000)
  ) %>% 
    slice(1) %>% 
    tidyr::unnest(col = .pred)
  predict(sr_fit, lung_test, type = "time")
  predict(sr_fit, lung_test, type = "linear_pred")
  predict(sr_fit, lung_test, type = "quantile") 
  predict(sr_fit, lung_test, type = "hazard", eval_time = c(100, 500, 1000)) %>% 
    slice(1) %>% 
    tidyr::unnest(col = .pred)
  ```
  
  </details>
